\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-09 design.tex
API + more images

\chapter{Design as a reaction to CDCS}

From its very inception, Skedge's functionality and visual design were driven by the shortcomings of CDCS. It was built \emph{bottom-up}, not \emph{top-down}, as every aspect of the application was either made as a reaction to a particular grievance in CDCS or as the natural evolution of an existing feature. Skedge is thus rooted in \emph{usability} derived from real need, not mere conjecture along the question ``what could students want?''. Its success with students, shown in Chapter 4, demonstrates that this usability extends beyond my own standard and can fulfill the various discovered use-cases of students in general.

@@

CDCS is an old system.

@@

- Can use back button
- Can send a link to a course or search

- Better UX
- Data is centralized

- Important nowadays
- Mobile traffic stat or smth

- Important nowadays, extends student possibility
- JSON
- Brief demo of API

@@

@@

>>>>

\chapter{Design in reaction to CDCS}

From its very inception, Skedge's functionality and visual design were driven by the shortcomings of CDCS. It was built \emph{bottom-up}, not \emph{top-down}---every aspect of the application was either made as a reaction to a particular grievance in CDCS or as the natural evolution of an existing feature. Skedge is thus rooted in \emph{usability} derived from real need, not mere conjecture along the question ``what could students want?''. Its success with students, shown in Chapter 4, demonstrates that this usability extends beyond my own standard and can fulfill the various discovered use-cases of students in general.

@@

CDCS is an old system, relatively speaking, and its recent development has been stagnant. It launched in 2009, seven years ago, and has hardly changed since. Figure \ref{fig:cdcs2010} shows CDCS in July 2010, which, besides the addition of a few search fields, is identical to its current version. Since its introduction in 2009, we have seen the rise of mobile devices into ubiquity, a boom in ``hacker culture'' and public APIs, and the capability for standalone web applications to be as sophisticated and dynamic as desktop-class applications without the aid of browser extensions.

\begin{figure}[ht]
  \centering
    \fbox{
      \includegraphics[width=10cm]{images/cdcs/2010}
    }
  \caption{CDCS in July 2, 2010, courtesy of \emph{Archive.org}}
  \label{fig:cdcs2010}
\end{figure}

- Important nowadays

- Mobile traffic stat or smth

\begin{figure}[ht]
  \centering
  \begin{tabular}{c c}
    \begin{subfigure}[h]{4cm}
      \centering
      \includegraphics[width=1.00\textwidth]{images/cdcs/mobile}
      \caption{CDCS} \label{fig:cdcs-mobile}
    \end{subfigure}
    \begin{subfigure}[h]{3.9cm}
      \centering
      \includegraphics[width=1.00\textwidth]{images/skedge/mobile}
      \caption{Skedge} \label{fig:sk-mobile}
    \end{subfigure}
  \end{tabular}
  \caption{CDCS and Skedge running on a mobile device}
\end{figure}

With the increasing number of attendees at University of Rochester's hackathons, it is clear that the University's ``hacker culture'' is growing (e.g. more students collaborating to build side-projects that integrate resources and servies often benefitting the student community), and projects that include the University's course catalog are becoming more common. Open-source and open-information services greatly help to foster such innovation, and having public APIs is essential toward this end.

Skedge provides a public JSON API at the root URL \url{http://www.skedgeur.com/api/}, made at the request of a student that was interested in using its course data, and the API has already been used in projects by several other student groups. The endpoints included are \url{/api/courses?q=query} (Skedge's query language---described in detail in section 2.3---is supported here), \url{/api/departments?q=optional_query}, and \url{/api/instructors?q=optional_query}.

- Better UX

- Data is centralized

@@

- Can use back button

- Can send a link to a course or search

@@

- More concise, space efficient (collapsable)
- Eliminates redundancy of same stuff (instructor, description, course title, etc)
- Don't have to pay more attention that you should to whether it's a different course or the same one

Note that in Figure \ref{fig:cdcs-sections}, the first two boxes are sections for the same course, and the next two are labs for that course. Four more lab sections and \emph{twenty} more workshop sessions for that same course follow below the truncated screenshot. Figure \ref{fig:sk-sections} demonstrates how this information can be conveyed more concisely.

\begin{figure}[ht]
  \centering
  \begin{tabular}{c c}
    \begin{subfigure}[h]{6cm}
      \centering
      \fbox{
        \includegraphics[width=1.00\textwidth]{images/cdcs/sections}
      }
      \caption{Ungrouped sections in CDCS} \label{fig:cdcs-sections}
    \end{subfigure}
    \hspace{15pt}
    \begin{subfigure}[h]{7cm}
      \centering
      \fbox{
        \includegraphics[width=1.00\textwidth]{images/skedge/sections}
      }
      \caption{Grouped sections in Skedge} \label{fig:sk-sections}
    \end{subfigure}
  \end{tabular}
  \caption{Section presentation on CDCS and Skedge}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \fbox{
    \includegraphics[width=8cm]{images/skedge/hover}
  }
  \caption{Hoverable and clickable course and instructor mentions in Skedge} \label{fig:sk-hover}
\end{figure}

### 2016-04-09 introduction.tex
Remove unneeded files
API + more images

@@

@@

\begin{figure}[ht]
    \centering
        \begin{subfigure}[h]{14cm}
            \centering
            \includegraphics[width=1.00\textwidth]{images/cdcs}
        \end{subfigure}\\
        \vspace{20pt}\\
        \begin{subfigure}[h]{15cm}
            \centering
            \includegraphics[width=1.00\textwidth]{images/skedge}
        \end{subfigure}
        \vspace{20pt}\\
    \caption{CDCS (top) and Skedge (bottom) for the search query {\tt csc}.}
\end{figure}

>>>>

%%%

@@

\label{fig:cdcs-index}

\subsection{``Better CDCS''}

\begin{figure}[ht]
    \centering
    \fbox{
        \includegraphics[width=1.00\textwidth]{images/cdcs/better}
    }
    \caption{Better CDCS, a separate browser extension that embeds buttons into the CDCS course results interface, allowing users to add courses to a locally-stored schedule}
    \label{fig:cdcs-better}
\end{figure}

%%%

@@

Skedge is a website I developed in 2014 and have been maintaining and developing since.

\ref{fig:sk-index}

\begin{figure}[ht]
    \centering
        \begin{subfigure}[h]{14cm}
            \centering
            \fbox{
                \includegraphics[width=1.00\textwidth]{images/cdcs/index}
            }
            \caption{CDCS}
            \label{fig:cdcs-index}
        \end{subfigure}\\
        \vspace{10pt}\\
        \begin{subfigure}[h]{14cm}
            \centering
            \fbox{
                \includegraphics[width=1.00\textwidth]{images/skedge/index}
            }
            \caption{Skedge}
            \label{fig:sk-index}
        \end{subfigure}\\
        \vspace{20pt}\\
    \caption{CDCS and Skedge for the search query {\tt csc}}
\end{figure}
